Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-14 prop_letter.tex
prop_letter.tex Fix typos...

The effect of finite precision and imperfections on contextuality and the
Kochen-Specker theorem is shown to have a resolution in terms of our QIVPM framework.  
To proceed, we use a formulation of the ``Mermin-Peres square'' \nb\cite{peres1995quantum,Mermin1990Simple} that uses the
expectation value of a physical observable with respect
to a QIVPM, where the interval-valued
expectation value is consistent with the expectation value of the
same observable in conventional quantum mechanics with infinite resources. We show that, 
as long as errors and uncertainties remain smaller that a particular value, the
Kochen-Specker theorem remains valid. In other words, we established a rigorous bound for 
its validity and, therefore, the limits for physical reality to remain contextual.

@@

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM\nb$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator\nb$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  ($P_0P_1=P_1P_0$)
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints\nb(\ref{eq:QIVPM-constraints}) are the direct
counterpart of the corresponding ones for conventional interval probability
measures.
With the understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
a direct counterpart of Eq.~(\ref{eq:classicalconvex}).

>>>>

The effect of finite precision and imperfections on contextuality and the
Kochen-Specker theorem is shown to have a resolution in terms of our QIVPM framework.  
To proceed, we use a formulation of the ``Mermin-Peres square'' \nb\cite{peres1995quantum,Mermin1990Simple} that uses the
expectation value of a physical observable with respect
to a QIVPM, where the interval-valued
expectation value is consistent with the expectation value of the
same observable in conventional quantum mechanics with infinite resources. We show that, 
as long as errors and uncertainties remain smaller than a particular value, the
Kochen-Specker theorem remains valid. In other words, we established a rigorous bound for 
its validity and, therefore, the limits for physical reality to remain contextual.

@@

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM\nb$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator\nb$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  ($P_0P_1=P_1P_0$)
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints, Eq.\nb(\ref{eq:QIVPM-constraints}), are the direct
counterpart of the corresponding ones for conventional interval probability
measures.
With the understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
a direct counterpart of Eq.~(\ref{eq:classicalconvex}).
